---
title: "Ted Talks"
author:
- "Dom Gorecki"
- "George Prentice"
- "Sarah Trostle"
- "Megan Calverley"
date: "5/25/2019"
output: html_document
---

```{r setup, include=FALSE}
ted_main <- read.csv("data/ted_main.csv", stringsAsFactors = FALSE)
source("scripts/summary.R")
source("scripts/table.R")
source("scripts/chart_one.R")
source("scripts/chart_two.R")
source("scripts/chart_three.R")
```

## Introduction


***

## Summary

***

## Table

***

## Chart One


## Chart Two

***

## Ted Talk Ratings
Viewers have the ability to choose up to three adjectives from a list when they
rate videos on TED's website. The following chart explores how often users
choose each adjective when leaving a rating. It also explores the popularity of
'postive' vs. 'negative' adjectives in ratings.

The chart reveals the most popular adjective chosen by users was **"Inspiring"**
while the least popular was **"Confusing"**. Of the positive ratings,
**"Jaw-dropping"** was the least popular. Of the negative ratings,
**"OK"** was the most popular. In general, positive ratings were chosen more
frequently than negative ratings. This could be partially due to the fact that
TED offers less options for negative ratings than positive.

of these adjectives
```{r ratings_plot, echo = FALSE, warning = FALSE}
ratings_plot(ted_main)
```