---
title: "Ted Talks"
author: "Megan Calverley"
date: "5/20/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("scripts/table.R")
```

## General Overview

There are a number of metrics that Ted Talks measure to gauge each talk's success. Below is a table of the top ten talks based on view count. In the table you will find the date the talk was filmed, the title with a link to the talk, the speaker's name, the tags associated with the talk, the number of languages that the talk is available in, the number of comments on the video and the number of views. 

```{r table, echo=FALSE}
kable(table, "html", col.names = c("Date", "Title", "Speaker", "Tags", "Languages", "Comments", "Views")) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = TRUE) %>% column_spec(1, width = "10em")
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
